% arara: xelatex
% arara: xelatex
% arara: xelatex

% options:
% thesis=B bachelor's thesis
% thesis=M master's thesis
% czech thesis in Czech language
% english thesis in English language
% hidelinks remove colour boxes around hyperlinks

\documentclass[thesis=M,english]{prefs/FITthesis}[2019/03/06]

% \usepackage{subfig} %subfigures
% \usepackage{amsmath} %advanced maths
% \usepackage{amssymb} %additional math symbols

\usepackage[utf8]{inputenc}

\usepackage{graphicx} %graphics files inclusion
% \usepackage{amsmath} %advanced maths
% \usepackage{amssymb} %additional math symbols

\usepackage{dirtree} %directory tree visualisation
\usepackage{subfig} %image side by side
\usepackage{todonotes} %todo
\usepackage{url}
\usepackage{textcomp} %degree symbol
\usepackage{color, colortbl} %color, table color
\usepackage{enumitem} %lists
\usepackage{float} %for H option in figures
\usepackage{array} %table aligment       
\usepackage{amsmath} %cases
\usepackage{amssymb}
\usepackage{svg} %svg
\usepackage{scrextend}
\usepackage{multirow}
\usepackage[ruled,vlined]{algorithm2e}
\addtokomafont{labelinglabel}{\sffamily}


\definecolor{LightCyan}{rgb}{0.88,1,1}
\definecolor{Blue}{rgb}{0.30980, 0.50588, 0.73725}
\definecolor{White}{rgb}{1, 1, 1}

% list of acronyms
\usepackage[acronym,nonumberlist,toc,nopostdot,numberedsection=autolabel,nomain]{glossaries}
\makeglossaries
\newcommand{\tg}{\mathop{\mathrm{tg}}} %cesky tangens
\newcommand{\cotg}{\mathop{\mathrm{cotg}}} %cesky cotangens

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
\department{Department of Applied Mathematics}
\title{Vehicle Routing Problem with Time Windows solved via Machine Learning and Optimization Heuristics}
\authorGN{Adam} %author's given name/names
\authorFN{Zvada} %author's surname
\authorWithDegrees{Bc. Adam Zvada} %author's name with academic degrees
\author{Adam Zvada} %author's name without academic degrees
\supervisor{doc. Ing. Pavel Kordík, Ph.D.}
\acknowledgements{
This is giving me the remarkable opportunity to express many thanks to the Big Bang for all its kindness in creating our space-time just right.

Great thanks also to my supervisor doc. Ing. Pavel Kordík, Ph.D. for all his help, time and advice.
}
\abstractCS{
Pro řešení vehicle routing problému byly navrženy nové přístupy v oblasti strojového učení, ale téměř žádná pozornost nebyla věnována variantě vehicle routing problému s časovými okny s mírným omezením (VRPTW). I přesto, že tato varianta je nutná řešit v každém produkčním řešení plánovacího logistického systému.

Tato práce navrhuje novou metodu řešení VRPTW pomocí hlubokého posilovaného učení. Model je postaven na architektuře Transformer využívající Graph Attention Network pro vložení vstupní instance. Model používá nově navrženou funkci odměny, která zahrnuje omezení časových oken. Práce také zkoumá další metaheuristické metody pro řešení VRPTW, které slouží ke vyhodnocení výsledného modelu.

Výsledkem této práce je end-to-end model hlubokého učení, který řeší VRPTW, který ale stále předčí metaheuristiké metody.
}
\abstractEN{
A novel approaches in the field of machine learning has been proposed to solve the vehicle routing problem, but yet a variant of vehicle routing with soft constrained time windows has received almost no attention. Even though it is a must for any production ready logistics planner.

This thesis proposes a new method for solving a vehicle routing problem with soft constrained time windows (VRPTW) using deep reinforcement learning. The model is built upon Transformer architecture utilizing Graph Attention Network for embedding the input instance. The model is using the proposed reward function that incorporates the time window constraint. The thesis also explores other metaheuristics methods for solving VRPTW, which is used to benchmark the model performance. 

The result of this thesis is end-to-end deep learning model solving VRPTW but it is still outperformed by metaheuristics solvers.
}
\placeForDeclarationOfAuthenticity{Prague} %where you have signed the declaration
\keywordsCS{vehicle routing problém, časová okna, vrptw, hluboké posilované učení, umělá inteligence, strojové učení, transformer, graph attention network\newpage}
\keywordsEN{vehicle routing problem, time windows, vrptw, deep reinforcment learning, artificial intelligence, machine learning, transformer, graph attention network}
\declarationOfAuthenticityOption{5} %select as appropriate, according to the desired license

\newacronym{ai}{AI}{artificial intelligence}
\newacronym{vrp}{VRP}{vehicle routing problem}
\newacronym{cvrp}{CVRP}{capacitated vehicle routing problem}
\newacronym{vrptw}{VRPTW}{vehicle routing problem with time windows}
\newacronym{tsp}{TSP}{traveling salesman problem}
\newacronym{ml}{ML}{machine learning}
\newacronym{pdp}{PDP}{Pick and Deliver}
\newacronym{vrppd}{VRPPD}{vehicle routing problem with pick and deliver}
\newacronym{rl}{RL}{reinforcement learning}
\newacronym{mha}{MHA}{Multi-head Attetntion}
\newacronym{gat}{GAT}{Graph Attention Network}
\newacronym{gcn}{GCN}{Graph Convolution Networks}
\newacronym{lns}{LNS}{Large Neighborhood Search}
\newacronym{alns}{ALNS}{Adaptive Large Neighborhood Search}

\begin{document}
    \input{src_text/00_introduction.tex}
    \input{src_text/01_intro_to_vrp.tex}
    \input{src_text/02_theoretical_background.tex}
    \input{src_text/03_vrptw_optimization.tex}
    \input{src_text/04_vrptw_ai.tex}
    \input{src_text/05_implementation.tex}
    \input{src_text/06_evaluation.tex}
    \input{src_text/07_conclusion.tex}
    
    % bibliography
    \bibliographystyle{prefs/iso690}
    \bibliography{ref}
    
    \appendix
    
    % acronyms
    \printglossaries
    
    % media contents
    \chapter{Media contents}\label{app:CDcontent}
    \begin{figure}
    	\dirtree{%
    	    .1 readme.txt\DTcomment{introductionary instructions}.
    		.1 rl-am-vrptw\DTcomment{the directory of VRPTW using deep learning}.
    		.2 README.md\DTcomment{the directory with example sequence from dataset}.
    		.2 rl-am-vrptw\DTcomment{source code of network}.
    		.1 godeliver-planner\DTcomment{directory of optimization planners}.
    		.2 godeliver-planner\DTcomment{source code of planers}.
    		.2 benchmarking\DTcomment{source code for running benchmarks}.
    		.1 text\DTcomment{the thesis text directory}.
    		.2 thesis\DTcomment{the directory of \LaTeX{} source codes of the thesis}.
    		.2 thesis.pdf\DTcomment{the Diploma thesis in PDF format}.
    	}
    \end{figure}
    

\end{document}

